% Cover letter using letter.sty
%\documentclass{letter} % Uses 10pt
\documentclass{cover-letter}
\usepackage{cover-letter}

% ============================
% Editor & Journal Info.
% ============================
\def\EditorFirstName{John}
\def\EditorLastName{Smith}
\def\EditorName{\EditorFirstName~\EditorLastName}
\def\EditorTitle{Editor-in-Chief, Managing Editor, Co-Editors-in-Chief}
\def\JournalName{Journal of XXX YYY ZZZ} % position
\def\JournalAddress{Address 1} % company

% =========================
% Paper Info.
% =========================
\def\PaperTitle{PAPER TITLE}
\def\YourName{YOUR NAME}
\def\YourEmail{YOUR Email}
\def\YourTitle{YOUR TITLE}
\def\InstitutionName{INSTITUTION NAME}
\def\InstitutionAddress{INSTITUTION ADDRESS}

\begin{document}

\date{October~21.~1999}

\begin{letter}{Dr./Mr./Ms. \EditorName \\
\EditorTitle \\
\JournalName \\
\JournalAddress}

\CoverLetterHeader

\opening{Dear Dr./Mr./Ms. \EditorLastName:} 

PARAGRAPH ONE: State reason for letter, name the position or type of work you are applying for and identify source from which you learned of the opening.
(i.e. Career Development Center, newspaper, employment service, personal contact). 

PARAGRAPH TWO: Indicate why you are interested in the position, the company, its products, services - above all, stress what you can do for the employer.
If you are a recent graduate, explain how your academic background makes you a qualified candidate for the position.
If you have practical work experience, point out specific achievements or unique qualifications.
Try not to repeat the same information the reader will find in the resume.
Refer the reader to the enclosed resume or application which summarizes your qualifications, training, and experiences.
The purpose of this section is to strengthen your resume by providing details which bring your experiences to life. 

PARAGRAPH THREE: Request a personal interview and indicate your flexibility as to the time and place.
Repeat your phone number in the letter and offer assistance to help in a speedy response.
For example, state that you will be in the city where the company is located on a certain date and would like to set up an interview.
Or, state that you will call on a certain date to set up an interview.
End the letter by thanking the employer for taking time to consider your credentials. 

\closing{Sincerely yours,} 

\end{letter}

\end{document}